Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-02-17 manuscript/appendix.Rmd
working on appendix & repo organization
appendix
working on appendix

---
title: "Supplementary Information: Global patterns of forest autotrophic carbon fluxes"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene C. Muller-Landau, Kristina J. Anderson-Teixeira"
toc: true
toc_depth: 1
output: 
  pdf_document:
    fig_caption: yes

header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
---

@@

\newpage
# Table S1. Climate variable definitions and sources
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") 
```

@@

\newpage
# Figure S1. 
![](tables_figures/distribution_all_samples.png)

>>>>

---
title: "Supplementary Information: Global patterns of forest autotrophic carbon fluxes"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene C. Muller-Landau, Kristina J. Anderson-Teixeira"
output: 
  pdf_document:
    fig_caption: yes

header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[table]{labelformat=empty}
                  \captionsetup[figure]{labelformat=empty}
---

@@

\listoftables
\listoffigures

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table S1. Climate variable definitions and sources", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") 
```

@@

\newpage
![Figure S1. Geographic distribution of samples for each of the nine FACF analyzed here.](tables_figures/distribution_all_samples.png)

\newpage
![Figure S2. Correlations among latitude and climate variables](tables_figures/climate_regressions.png)
